Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-21 draft.tex
merge

See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

@@

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras.
Then
\begin{itemize}
\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{itemize}
\end{thm}

@@

Existing work provides insight into and context for the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
Our approach leverages these results as follows to prove the theorem.
\begin{enumerate}
\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant. Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
\item  In particular, given an $E_n$ algebra $B$,  let ${\tt B}$ denote a strict prefactorization algebra modeling~$B$.
Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map ${\tt f}: {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras. 
\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but I'm not sure this plays nicely with the other strictification\dots}
\item From the map ${\tt f}$, we read off an $\fg$-action on ${\tt B}$ intertwining with the structure maps of ${\tt B}$. 
That is, we have a prefactorization algebra ${\tt B}_f$ taking values in the 1-category $\Ch(\Rep(\fg))$ of chain complexes of $\fg$-representations.
\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map
\[
\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
\]
such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict prefactorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks. 
\end{enumerate}
Hence it induces a weak equivalence of the associated $E_n$ algebras.

\owen{Some easy but important situations to examine:}
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

By Knudsen's results \cite{Knudsen}, we have the following explicit applications of our main theorem~\ref{thm: center}.

\owen{I think we should just work in $Ch(\RR)$ or $Ch(\CC)$ throughout.}

\begin{cor}\label{cor:centerfactorization}
Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
Then the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
\end{cor}

@@

\section{Background}

\owen{Add overview}

\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
\label{sec: en background}

\owen{Recall Jacob's results and what it means in conjunction with strictification.}

\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}

Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\begin{thm}
\label{T:En=Fac} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$.
\end{thm}

\subsection{Enveloping $E_n$ algebras of Lie algebras}
\label{sec: enveloping}

Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

@@

The second part of this result leads to the explicit models in our theorems.

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

\owen{\label{note on little model} Note that if we work with the colored operad of disks/boxes, then Poincar\'e lemma tells us that we can use the strict model $\cliel(\fg[-n])$ rather than the fatter model $\cliels(\Omega^*_c(U) \otimes \fg)$. I think Ben actually shows this too. This would be worth explaining because we can then use a much simpler strictification of $f$.}

\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
\label{sec: centralizer}

@@

We now turn to proving Theorem~\ref{thm: centralizer}.

\section{Strictifying the map $f: \UU_n \fg \to B$}

As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.

By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
\[
{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
\]

\owen{And now I'm really confused.}

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
 $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace. 
\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

@@

\brian{do you like this example?} \greg{I do !}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
\end{eg}

>>>>

See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

@@

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras that gives $B$
the structure of an $E_n$ algebra in $\fg$-modules\footnote{see Proposition~\ref{P:inducedEngModStruct}}. 
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{thm}

@@

Existing work gives us some insight into the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
\item In combination, we have an explicit characterization of the centralizer up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}

Our approach has the following steps:
\begin{enumerate}
\item Transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant. (First use Lurie to explain that we can work with the homotopy coherent version, and then invoke strictification theorems from the model category literature on operads.) 
\item In particular, explain why $B$ determines some prefactorization algebra that I'll also call~$B$. Explain how the map $f: \UU_n \fg \to B$ determines a $\fg$-action on $B$. That is, we can obtain a prefactorization algebra $B_f$ taking values in the 1-category of $\fg$-representations.
See Lemma \ref{L:inducedFacgModstruct}. 
\item Construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra", Lemma \ref{L:ClieFacDef}.
We then argue that it canonically fits into a centralizer diagram: there is a map of prefactorization algebras
\[
\clies(\Omega \otimes \fg, B_f) \otimes \UU_n \fg \to B_f
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$, see Lemma \ref{L:ComTriangCent}.
\item Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \cZ_f$ as strict prefactorization algebras.
\item Verify that this map is a quasi-isomorphism on disks, Lemma \ref{L:thetaquisondisk}.
Hence it induces a weak equivalence of the associated $E_n$ algebras. 
\end{enumerate}

Some easy but important situations to examine:
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

\owen{End of strategy}

By Knudsen's results \cite{Knudsen}, we have the following explicit interpretation of our main theorem~\ref{thm: center}, which is the second part of our main theorem.

\begin{cor}\label{cor:centerfactorization}
Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
\end{cor}

@@

\section{Enveloping $E_n$ algebras of Lie algebras}

Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

@@

The second part of this result leads to the explicit models in our theorems.
Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.

\begin{thm}
\label{T:En=Fac} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
\end{thm}

\begin{rmk}
 It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
 $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
 $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
\[
\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
\]
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.

\brian{let's start with a strict representative $B$. 
So we have an actual locally constant factorization algebra.}

\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
 \brian{How about $\ul{B}$ instead?}

\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace.

\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

\section{Centralizers of maps of $E_n$ algebras and the derived center}
\label{sec: centralizer}

@@

We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.

@@

\brian{do you like this example?} \greg{I do !}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section \ref{??}.

On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.

Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
\end{eg}
